### 2023-05-02 application.tex
up

We now consider the set $\Bad \setminus (\pred^{\leq k}(q_{j_1}(\omega)) \cup \ldots \pred^{\leq k}(q_{j_\ell}(\omega)) )$.
\mathieu{Is it actually possible to check whether or not it is finite ?}
If it is finite then we can check for every element in it whether or not it is possible to reach from it $\Safe$ in $k$ or less steps.
If it is infinite then
$k$-resilience does not hold.
\mathieu{... because it can only be infinite if there is some kind of unbounded $q(BIG)$ that is not in any of the $\pred^{\leq k}(q_{j_1}(\omega))$ and since from this $q(BIG)$ it's not possible to reach the `smaller' elements of $\Safe$ in $k$ or less steps then it's not possible at all to reach $\Safe$ in $k$ or less steps ergo $k$-resilience does not hold.}
\end{proof}

>>>>

We now consider the set $\Bad \setminus (\pred^{\leq k}(q_{j_1}(\omega)) \cup \ldots \pred^{\leq k}(q_{j_\ell}(\omega)) )$.
% \mathieu{Is it actually possible to check whether or not it is finite ?}
% If it is finite then w
We can check for the elements in it whether or not it is possible to reach from it $\Safe$ in $k$ or less steps.
If the set is finite then we stop the procedure once we have checked for every element.
If it is infinite then
$k$-resilience does not hold 
and there exists an element of the form $q(u)$
that is in $\Bad$ but not in any of the $\pred^{\leq k}(q_{j_i}(\omega))$
for which it is not possible to reach the `smaller' elements of $\Safe$ in $k$ or less steps and thus it is not possible at all to reach $\Safe$ in $k$ or less steps.
\end{proof}
